---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Earthquakes induced by Gas Exploration in The Netherlands 

#### *Maaike Miedema, June 14, 2017*


```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library (leaflet)

allInduced <- read.csv("all_induced.csv")
induced<- filter(allInduced, MAG>0)

mapInduced <-induced %>% 
        leaflet() %>%
        addTiles() %>% 
        addCircles(data=induced, lng=~LON, lat=~LAT, weight=1, radius = 7*sqrt(30^induced$MAG), 
                   col = "darkred", popup = paste("magnitude: ",as.character(induced$MAG)))
setView(mapInduced,lng = 5.7, lat = 53.1, zoom = 8)

```

  
####
***About the map***  
Gas exploration causes subsidense and earthquakes, leading to damage, especially in the North Eastern part of The Netherlands. This map shows registered earthquakes induced by gas exploration, 1986 - present. The magnitude is given at Richter scale. This is a logarithmic scale and the area of the circles is set relative to the energy released.
  
  
***Source of data***  
Data downloaded June 14, 2017 from the site of the Royal Dutch Meteorological Institute  
http://knmi.nl/kennis-en-datacentrum/dataset/aardbevingscatalogus, file: all_induced.csv.
